Toxic Code Snippets on Stack Overflow

### 2017-11-07 cloverflow-tse/cloverflow.tex
Layout improvements.

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones''.
There are two directions in creating online code clones: (1) code is cloned from
a software project to a Q\&A website as an example; or (2) code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3) code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.~clones between software systems, online code clones
can lead to license violations, bug propagation, introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.

@@

Toxic code snippets mean code snippets that are harmful for reuse and, in
several cases, are caused by online code cloning. Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1) outdated or (2) violating their original software
license. Outdated code snippets
can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license , e.g.~GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

	\textit{1) How often are Stack Overflow
		answerers aware of the outdated code when
		they answer a question on Stack Overflow?}

@@

\textbf{EX: External Sources.} We found 199 clone pairs from external sources to
Stack Overflow. After consolidating duplicated SO snippets due to multiple
intra-clone instances in Qualitas, we obtained 111 EX pairs. We found
evidence of copying from an external source to both Stack
Overflow and Qualitas in 50 pairs. Each of the pairs contains
statement(s) pointing to the original external location of the cloned
code in Qualitas and Stack Overflow. In addition, we found evidence
of copying from an external source to Stack Overflow, but not in
Qualitas, in 61 pairs. 
Our
analysis shows that the external sources fall into six groups as displayed in
\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
from source code of Java SDK (e.g.~\textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
18 pairs from websites, 15 pairs from open
source systems not in Qualitas (e.g.~\textsf{Mozilla
	Rhino}), 11 pairs from Java official documentations from Sun
Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
project. For example, Stack Overflow Post 9549009 contains a code comment saying
\textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.

@@

The outdated online code clones cause problems ranging from uncompilable code
(due to modifications and different API usage in the outdated code) to
the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without
awareness from developers. Moreover, an outdated code with a defect (e.g.~a race
condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
Although Stack Overflow has a voting mechanism that may mitigate this issue, the
accepted answer is still used by naive developers who copy and reuse the
outdated code.

@@

We asked the remaining 200 participants for the origins of code snippets in
their answers. We provided six locations including the answerer's personal
projects, the answerer's company projects, open source projects, writing the
code from scratch, copying and modifying the code from the question, and others
(e.g.~code that are copied from other questions or answers on Stack Overflow)
and we asked them to rate how often they copied the code from these locations. The
results are shown in \Cref{fig:survey_snippet_source}. Looking at the Very
Frequently section, we can see that the answerers mainly write new code from
scratch (71) or copy and modify the code snippets from the question for each answer (56),
while fewer numbers are from other sources including their personal projects
(42), their company projects (10), and open source projects (14). Although
copying from open source projects is not the most popular choice, the answerers
still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
participants who frequently, occasionally, and rarely copied code snippets from
open source projects.

@@

Many users either declare their snippets to be public domain, or they grant
additional licenses, e.g. Apache 2.0 or MIT/Expat.

@@

%We discovered two issues regarding code snippets on Stack Overflow in this
% study: (1)  outdated online clones on Stack Overflow and (2) missing or
% incompatible license in Stack Overflow snippets.
%that there is a considerable amount of cloned code between Stack Overflow that
% are cloned from 111 projects in the Qualitas corpus. 64 clone pairs are
% outdated and 358 snippets have incompatible software licenses to their
% originals.
Our study discovers links from code in open source projects to code snippets on
Stack Overflow using clone detection techniques. These links enable us to
discover toxic code snippets with outdated code or licensing problems. 
The links can be exploited further to mitigate the problems of reusing outdated online clones and
incompatible license on Stack Overflow code snippets. We propose the following
actionable items:

@@

%\section{Future Work}
%Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow. The similar study of outdated code and software licensing violation can be repeated. It is interesting to compare the findings among different programming languages. Moreover, other popular software project corpora (e.g.~GitHub) can also be included to increase generalisation of the findings.
%
%We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool. The tool should incorporate a scalable clone detection method of locate similar code from programming Q\&A websites such as Stack Overflow and online code repositories like GitHub. It analyses a software project under development and reports clones that are copied from Stack Overflow. The reported clones have traces to their origins in open source projects or websites along with their freshness (fresh/outdated/dead) so that the developer of the project can be aware of changes made to the copied code snippets. Lastly, the license of the original source code is also reported so the developer can make an informed decision of whether he or she will incorporate that code snippet into their own project.

>>>>

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones''.
There are two directions in creating online code clones: (1)~code is cloned from
a software project to a Q\&A website as an example; or (2)~code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3)~code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.~clones between software systems, online code clones
can lead to license violations, bug propagation, introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.

@@

Toxic code snippets mean code snippets that are harmful for reuse and, in
several cases, are caused by online code cloning. Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated or (2)~violating their original software
license. Outdated code snippets
can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license , e.g.\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

	\textit{1)~How often are Stack Overflow
		answerers aware of the outdated code when
		they answer a question on Stack Overflow?}

@@

\textbf{EX: External Sources.} We found 199 clone pairs from external sources to
Stack Overflow. After consolidating duplicated SO snippets due to multiple
intra-clone instances in Qualitas, we obtained 111 EX pairs. We found
evidence of copying from an external source to both Stack
Overflow and Qualitas in 50 pairs. Each of the pairs contains
statement(s) pointing to the original external location of the cloned
code in Qualitas and Stack Overflow. In addition, we found evidence
of copying from an external source to Stack Overflow, but not in
Qualitas, in 61 pairs. 
Our
analysis shows that the external sources fall into six groups as displayed in
\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
from source code of Java SDK (e.g.\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
18 pairs from websites, 15 pairs from open
source systems not in Qualitas (e.g.\ \textsf{Mozilla
	Rhino}), 11 pairs from Java official documentations from Sun
Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
project. For example, Stack Overflow Post 9549009 contains a code comment saying
\textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.

@@

The outdated online code clones cause problems ranging from uncompilable code
(due to modifications and different API usage in the outdated code) to
the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
subtle change (e.g.\ \Cref{fig:before-after}) may be copied and reused without
awareness from developers. Moreover, an outdated code with a defect (e.g.\ a race
condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
Although Stack Overflow has a voting mechanism that may mitigate this issue, the
accepted answer is still used by naive developers who copy and reuse the
outdated code.

@@

We asked the remaining 200 participants for the origins of code snippets in
their answers. We provided six locations including the answerer's personal
projects, the answerer's company projects, open source projects, writing the
code from scratch, copying and modifying the code from the question, and others
(e.g.\ code that are copied from other questions or answers on Stack Overflow)
and we asked them to rate how often they copied the code from these locations. The
results are shown in \Cref{fig:survey_snippet_source}. Looking at the Very
Frequently section, we can see that the answerers mainly write new code from
scratch (71) or copy and modify the code snippets from the question for each answer (56),
while fewer numbers are from other sources including their personal projects
(42), their company projects (10), and open source projects (14). Although
copying from open source projects is not the most popular choice, the answerers
still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
participants who frequently, occasionally, and rarely copied code snippets from
open source projects.

@@

Many users either declare their snippets to be public domain, or they grant
additional licenses, e.g.\ Apache 2.0 or MIT/Expat.

@@

%We discovered two issues regarding code snippets on Stack Overflow in this
% study: (1)~outdated online clones on Stack Overflow and (2)~missing or
% incompatible license in Stack Overflow snippets.
%that there is a considerable amount of cloned code between Stack Overflow that
% are cloned from 111 projects in the Qualitas corpus. 64 clone pairs are
% outdated and 358 snippets have incompatible software licenses to their
% originals.
Our study discovers links from code in open source projects to code snippets on
Stack Overflow using clone detection techniques. These links enable us to
discover toxic code snippets with outdated code or licensing problems. 
The links can be exploited further to mitigate the problems of reusing outdated online clones and
incompatible license on Stack Overflow code snippets. We propose the following
actionable items:

@@

%\section{Future Work}
%Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow. The similar study of outdated code and software licensing violation can be repeated. It is interesting to compare the findings among different programming languages. Moreover, other popular software project corpora (e.g.\ GitHub) can also be included to increase generalisation of the findings.
%
%We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool. The tool should incorporate a scalable clone detection method of locate similar code from programming Q\&A websites such as Stack Overflow and online code repositories like GitHub. It analyses a software project under development and reports clones that are copied from Stack Overflow. The reported clones have traces to their origins in open source projects or websites along with their freshness (fresh/outdated/dead) so that the developer of the project can be aware of changes made to the copied code snippets. Lastly, the license of the original source code is also reported so the developer can make an informed decision of whether he or she will incorporate that code snippet into their own project.
